An enhancer code compendium of early human neural and neural crest development

### 2025-04-22 manuscript.tex
acknowledgments

\begin{figure}[b!]
  \ContinuedFloat
  \caption*{\rule{\linewidth}{0.4pt}}
  \caption{
    (Continued) 
    \textbf{b}, Boxplots of the expression of \textit{SHH} in organoid (top) and embryo (bottom) across different dorso-  ventral topics ($n_{topic 33}$ = 4,571, $n_{topic 38}$ = 4,521, $n_{topic 36}$ = 6,120, $n_{topic 54}$ = 2,808, and $n_{topic 48}$ = 5,390 for organoid cells;
      and $n_{topic 34}$ = 637, $n_{topic 38}$ = 1,093, $n_{topic 79}$ = 3,939, $n_{topic 88}$ = 1,861, and $n_{topic 58}$ = 1,773 for embryo cells).  With n representing the number of cells.
    \textbf{c}, Chromatin accessibility in organoid (top) and embryo (bottom) across dorso-ventral topics for locus chr7:155,799,664-155,827,483 ; hg38. SFPE2 and SFPE1 are highlighted. 
    \textbf{d}, Enhancer reporter assay in chicken embryo. Blue is DAPI, pink is constitutive electroportion control,
    green is GFP driven by SFPE1 enhancer.
    \textbf{e}, Nucleotide contribution scores for SFPE2 (left) and SFPE1 (right) for organoid topic 33 (top) and embryo topic 34 (bottom). 
    \textbf{f}, Code table showing average contribution score of pattern instances for each dorso-ventral topic. Contribution scores for $DeepNeuralTube^o$ are not outlined. Contribution scores for $DeepNeuralTube^e$ are outlined and negated. 
    \textbf{g}, Heatmap showing the maximum normalized contribution score for each of the top 1,000 regions per topic (y-axis) and pattern (x-axis) for dorso-ventral topics. 
    \textbf{h}, Heatmap showing scaled expression of transcription factors corresponding to identified patterns in organoid (left) and embryo (right) dorso-ventral topics. 
    \textbf{i}, Heatmap showing Jaccard index of regions based on the presence of instances of the identified patterns. 
    \textbf{j}, Nucleotide contribution score for chr18:77367159-77367659; hg38 for organoid topic 33 (top) and embryo
    topic 34 (bottom).
    \textbf{k}, Prediction scores for chr18:77367159-77367659; hg38 for doros-ventral topics in organoid (top) and
    embryo (botto).
    \textbf{l}, Enhancer reporter assay in chicken embryo. Blue is DAPI, pink is constitutive electroportion control,
    green is GFP driven by chr18:77367159-77367659; hg38 enhancer.
}
\end{figure}

@@

@@

>>>>

\begin{figure}[b!]
  \ContinuedFloat
  \caption*{\rule{\linewidth}{0.4pt}}
  \caption{
    (Continued) 
    \textbf{b}, Boxplots of the expression of \textit{SHH} in organoid (top) and embryo (bottom) across different dorso-  ventral topics ($n_{topic 33}$ = 4,571, $n_{topic 38}$ = 4,521, $n_{topic 36}$ = 6,120, $n_{topic 54}$ = 2,808, and $n_{topic 48}$ = 5,390 for organoid cells;
      and $n_{topic 34}$ = 637, $n_{topic 38}$ = 1,093, $n_{topic 79}$ = 3,939, $n_{topic 88}$ = 1,861, and $n_{topic 58}$ = 1,773 for embryo cells).  With n representing the number of cells.
    \textbf{c}, Chromatin accessibility in organoid (top) and embryo (bottom) across dorso-ventral topics for locus chr7:155,799,664-155,827,483 ; hg38. SFPE2 and SFPE1 are highlighted. 
    \textbf{d}, Enhancer reporter assay in chicken embryo. Blue is DAPI, pink is constitutive electroportion control,
    green is GFP driven by SFPE1 enhancer.
    \textbf{e}, Nucleotide contribution scores for SFPE2 (left) and SFPE1 (right) for organoid topic 33 (top) and embryo topic 34 (bottom). 
    \textbf{f}, Code table showing average contribution score of pattern instances for each dorso-ventral topic. Contribution scores for $DeepNeuralTube^o$ are not outlined. Contribution scores for $DeepNeuralTube^e$ are outlined and negated. 
    \textbf{g}, Heatmap showing the maximum normalized contribution score for each of the top 1,000 regions per topic (y-axis) and pattern (x-axis) for dorso-ventral topics. 
    \textbf{h}, Heatmap showing scaled expression of transcription factors corresponding to identified patterns in organoid (left) and embryo (right) dorso-ventral topics. 
    \textbf{i}, Heatmap showing Jaccard index of regions based on the presence of instances of the identified patterns. 
    \textbf{j}, Nucleotide contribution score for chr18:77367159-77367659; hg38 for organoid topic 33 (top) and embryo
    topic 34 (bottom).
    \textbf{k}, Prediction scores for chr18:77367159-77367659; hg38 for doros-ventral topics in organoid (top) and
    embryo (bottom).
    \textbf{l}, Enhancer reporter assay in chicken embryo. Blue is DAPI, pink is constitutive electroportion control,
    green is GFP driven by chr18:77367159-77367659; hg38 enhancer. Scale bar represents \SI{500}{\micro\meter}
}
\end{figure}

@@

We thank Peter L\"onnerberg for preprocessing the human embryo data and making it available through EGA.

@@

% TODO: see https://www.cell.com/information-for-authors/star-supplemental-information
